---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

# Dining Preference Proportion Test in Campus

```{r}
data<-read.csv('C:/Users/geete/OneDrive/Desktop/sem3/Stats.csv',header=TRUE)
data
```

```{r}
group1_data <- subset(data, Category == 'Cafe By The Valley')
group2_data <- subset(data, Category != 'Cafe By The Valley')

group1_data
group2_data

```

```{r}
prop_group1 <- nrow(group1_data) / nrow(data)
prop_group2 <- nrow(group2_data) / nrow(data)
print(prop_group1)
print(prop_group2)
```

## p1 is the proportion of people who prefer Cafe By The Valley

## Null_Hypothesis= p1=0.5

#### Proportion of people who prefer Cafe By The Valley is 50% of the population

## Alternative_Hypothesis= p1\>0.5

#### Proportion of people who prefer Cafe By the Valley is more than 50% of the population

```{r}
result1<-prop.test(sum(data$Category=='Cafe By The Valley'),nrow(data),alternative='greater')
print(result1)
```

## since p-value is lesser than 0.5 , we reject null hypothesis

```{r}
contingency_table<-table(data$Category)
print(contingency_table)
```

## Contingency table shows us the count of each category

```{r}
table_result <- table(data$Category == 'Cafe By The Valley')
contingency_table <- matrix(c(table_result, 0), nrow = 2, byrow = TRUE)
fisher_test_result <- fisher.test(contingency_table)
print(fisher_test_result)


```

## Again the p-value is lesser than 0.5, therefore we reject null hypothesis

------------------------------------------------------------------------

------------------------------------------------------------------------
